---
title: "gottlieb_figures"
author: "Andrew McCormack"
date: "11/07/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

## R Markdown

```{r cars}
library(readxl)
library(readstata13)

# Function to convert factor to numeric
fac_to_num <- function(x) {
  as.numeric(levels(x))[x]
}

gottlieb_outcomes <- c("Economy", "Poverty", "Infrastructure",
                       "Health", "Water", "Education", "Agriculture",
                       "Violence", "Rights", "Services")
```


# 1) COMPARING COEFFICIENTS ON FEMALE FROM MODELS WITH AND WITHOUT AGE DIFFERENCES

```{r}
gottlieb_reg_age_diff <- read_dta("data_clean/gottlieb_clean/gottlieb_regs/gottlieb_reg_age_diff.dta")
gottlieb_reg_original <- read_dta("data_clean/gottlieb_clean/gottlieb_regs/gottlieb_reg_original.dta")
gottlieb_reg_age_diff_interviewer_gender <- read_dta("data_clean/gottlieb_clean/gottlieb_regs/gottlieb_reg_age_diff_interviewer_gender.dta")
```

```{r}
table(gottlieb_regs$eq)
```


```{r}
gottlieb_regs <- rbind(gottlieb_reg_original, gottlieb_reg_age_diff, gottlieb_reg_age_diff_interviewer_gender)
rm(gottlieb_reg_age_diff, gottlieb_reg_original, gottlieb_reg_age_diff_interviewer_gender)
gottlieb_regs

gottlieb_models_plot <- gottlieb_regs %>%
  # Keep only female coefficients
  filter(parm == "female") %>%
  # Generate variable to indicate which coefficients are from each of the two models
  mutate(model = case_when(grepl("_age_igender", eq) ~ "Controlling for age differences and interviewer gender", 
                           grepl("_age_diff", eq) ~ "Controlling for age differences",
                           TRUE ~ "Original model")) %>%
  # With `model` created, appended _age_diff can be removed
  mutate(eq = str_remove(eq, "_age_diff|_age_igender")) %>%
  # Gottlieb et al. don't plot "None"
  filter(eq != "None") %>%
  # Make factor so it is in same order as in Gottlieb et al. paper
  mutate(eq = fct_rev(factor(eq, levels = gottlieb_outcomes))) %>%
  ## PLOT
  ggplot(aes(eq, 
             estimate, 
             colour = model)) +
    theme_linedraw() +
    geom_point(position = position_dodge(width = 0.8)) +
    geom_errorbar(aes(ymin = min95, ymax = max95),
                  position = position_dodge(width = 0.8),
                  width = 0.5) +
    scale_colour_manual(values = c("firebrick3", "black",  "darkslategray3")) +
    coord_flip() +
    scale_y_continuous(breaks = seq(-0.04, 0.08, 0.02),
                     limits = c(-0.04, 0.09)) +
     theme(axis.title.y = element_blank(),
          legend.title = element_blank(),
          legend.position = "bottom",
          legend.text = element_text(size = 7),
          legend.key.width=unit(1,"line")) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    guides(colour = guide_legend(reverse = TRUE,
                                 ncol = 2),
           linetype = guide_legend(reverse = TRUE,
                                 ncol = 2)) +
    ylab("Impact of gender (female) on likelihood of policy domain prioritization \nSUR pooled OLS analysis with county fixed effects, 95% CIs")

ggsave("figs/gottlieb_figs/gottlieb_models_plot.png", gottlieb_models_plot, height = 4, width = 7)
```


# 2) Contrasts with just age differences

```{r pressure, echo=FALSE}
# Import tabulate
age_cats <- readLines("data_clean/gottlieb_clean/gottlieb_contrasts_age/age_diff_cat_levels.txt") %>%
  tibble() 

# Name column
names(age_cats) <- "cats"
  
# Separate column
age_cats <- age_cats %>%
  separate(cats, c("category", "percent"), sep = "\t") 

# First row is column names, so I remove
age_cats <- age_cats[2:nrow(age_cats), ]

# Category numbers
age_cats$category_number <- 1:nrow(age_cats)

age_cats <- age_cats %>%
  dplyr::select(category_number, category)
```


```{r}
contrast_files_age <- list.files("data_clean/gottlieb_clean/gottlieb_contrasts_age", pattern = ".xlsx")

contrasts_age <- lapply(paste0("data_clean/gottlieb_clean/gottlieb_contrasts_age/", contrast_files_age), 
                    read_xlsx) %>%
  # Transpose (messes up column names, fixed below)
  lapply(function(x) as.data.frame(t(as.matrix(x))))

# First row is column names, save this
contrast_col_names <- as.character(unlist(contrasts_age[[1]][1,]))
  
# Remove first row
contrasts_age <- lapply(contrasts_age, function(x) x[2:nrow(x), ]) 

# Fix names
for(i in 1:length(contrasts_age)) {
  names(contrasts_age[[i]]) <- contrast_col_names
  contrasts_age[[i]]$outcome <- str_remove(contrast_files_age, ".xlsx")[i]
}

# Rownames to column
contrasts_age <- lapply(contrasts_age, rownames_to_column)

# Name list according to model
names(contrasts_age) <- str_remove(contrast_files_age, ".xlsx")

rm(contrast_col_names, contrast_files)
```

Contrasts of interest are:

Both younger (r2) -> Interviewer older (r3)
Both older (r1) -> Interviewer younger (r4)

```{r}
# Rbind all list items together and clean up names
contrasts_age <- do.call("rbind", contrasts_age) %>%
  mutate(rowname = str_remove(rowname, ".age_diff_cat")) %>%
  mutate(outcome = str_remove(outcome, "both_older_contrast_|both_younger_contrast_")) %>%
  mutate(outcome = str_remove(outcome, "_age_diff"))

contrasts_age$rowname

contrasts_age <- contrasts_age[contrasts_age$rowname %in% c("r3vs2", "r4vs1"),]
```


```{r}
gottlieb_contrasts_age_plot <- contrasts_age %>%
  mutate(contrast = case_when(rowname == "r4vs1" ~ "Both older vs. Interviewer younger/respondent older",
                              rowname == "r3vs2" ~ "Both younger vs. Interviewer older/respondent younger")) %>%
  # Make factors as numeric
  mutate_if(is.factor, fac_to_num) %>%
  filter(outcome != "None") %>%
  mutate(outcome = fct_rev(factor(outcome, levels = gottlieb_outcomes))) %>%
  # Reverse contrast and CIs so the contrast is between 
  # the baseline and the counterfactual changed interviewer age/gender
  mutate(b = 0 - b,
         ll = 0 - ll,
         ul = 0 - ul) %>%
  # Make plot
  ggplot(aes(outcome, 
             b, 
             colour = contrast)) +
    theme_linedraw() +
    geom_point(position = position_dodge(width = 0.5)) +
    geom_errorbar(aes(ymin = ll, ymax = ul),
                  position = position_dodge(width = 0.5),
                  width = 0.3) +
    scale_colour_manual(values = c("firebrick3", "black")) +
    coord_flip() +
    scale_y_continuous(breaks = seq(-0.06, 0.06, 0.02),
                     limits = c(-0.06, 0.06)) +
     theme(axis.title.y = element_blank(),
          legend.title = element_blank(),
          legend.position = "bottom",
          legend.text = element_text(size = 7),
          legend.key.width=unit(3,"line")) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    guides(colour = guide_legend(reverse = TRUE,
                                 ncol = 1),
           linetype = guide_legend(reverse = TRUE,
                                 ncol = 1)) +
    ylab("Contrasts of likelihood of policy domain prioritization \nSUR pooled OLS analysis with county fixed effects, 95% CIs")

ggsave("figs/gottlieb_figs/gottlieb_contrasts_age_plot.png", gottlieb_contrasts_age_plot, height = 4, width = 8)
```



# 3) CONTRAST PLOTS WITH AGE AND GENDER

This is one method of finding out what the factor levels are. I save the tabulate results as a text file:

```{r pressure, echo=FALSE}
age_gender_cats <- readLines("data_clean/gottlieb_clean/gottlieb_contrasts_age_gender/age_diff_gender_cat_levels.txt") %>%
  tibble() 

# Name column
names(age_gender_cats) <- "cats"
  
# Separate column
age_gender_cats <- age_gender_cats %>%
  separate(cats, c("category", "percent"), sep = "\t") 

# First row is column names, so I remove
age_gender_cats <- age_gender_cats[2:nrow(age_gender_cats), ]

# Category numbers
age_gender_cats$category_number <- 1:nrow(age_gender_cats)

age_gender_cats <- age_gender_cats %>%
  dplyr::select(category_number, category)
```

## Import contrasts data

```{r}
contrast_files_age_gender <- list.files("data_clean/gottlieb_clean/gottlieb_contrasts_age_gender/", pattern = ".xlsx")

contrasts_age_gender <- lapply(paste0("data_clean/gottlieb_clean/gottlieb_contrasts_age_gender/", contrast_files_age_gender), 
                    read_xlsx) %>%
  # Transpose (messes up column names, fixed below)
  lapply(function(x) as.data.frame(t(as.matrix(x))))

# First row is column names, save this
contrast_col_names <- as.character(unlist(contrasts_age_gender[[1]][1,]))
  
# Remove first row
contrasts_age_gender <- lapply(contrasts_age_gender, function(x) x[2:nrow(x), ]) 

# Fix names
for(i in 1:length(contrasts_age_gender)) {
  names(contrasts_age_gender[[i]]) <- contrast_col_names
  contrasts_age_gender[[i]]$outcome <- str_remove(contrast_files_age_gender, ".xlsx")[i]
}

# Rownames to column
contrasts_age_gender <- lapply(contrasts_age_gender, rownames_to_column)

# Name list according to model
names(contrasts_age_gender) <- str_remove(contrast_files_age_gender, ".xlsx")

rm(contrast_col_names, contrast_files_age_gender)
```

Contrasts of interest are:

Both older, both female (r1) -> Both older, Int. male, resp. female (r4)
Both older, both female (r1) -> Interviewer younger, Int. male, resp. female (r16)

Both younger, both female (r5) -> Both younger, Int. male, resp. female (r8)
Both younger, both female (r5) -> Interviewer older, Int. male, resp. female (r12)

```{r}
# Rbind all list items together and clean up names
contrasts_age_gender <- do.call("rbind", contrasts_age_gender) %>%
  dplyr::mutate(rowname = str_remove(rowname, ".age_diff_gender_cat")) %>%
  dplyr::mutate(outcome = str_remove(outcome, "both_older_female_contrast_|both_younger_female_contrast_")) %>%
  dplyr::mutate(outcome = str_remove(outcome, "_age_gender"))
  
contrasts_age_gender <- contrasts_age_gender[contrasts_age_gender$rowname %in% c("r4vs1", 
                                   "r16vs1",
                                   "r8vs5", 
                                   "r12vs5"), ]
```

```{r}
gottlieb_contrasts_age_gender_plot <- contrasts_age_gender %>%
  mutate(contrast = case_when(rowname == "r4vs1" ~ "Both older, both female vs. \nBoth older, Int. male/resp. female",
                              rowname == "r16vs1" ~ "Both older, both female vs. \nInterviewer younger, Int. male/resp. female",
                              rowname == "r8vs5" ~ "Both younger, both female vs. \nBoth younger, Int. male/resp. female",
                              rowname == "r12vs5" ~ "Both younger, both female vs. \nInterviewer older, Int. male, resp. female")) %>%
  # Make factors as numeric
  mutate_if(is.factor, fac_to_num) %>%
  filter(outcome != "None") %>%
  mutate(outcome = fct_rev(factor(outcome, levels = gottlieb_outcomes))) %>%
  # Reverse contrast and CIs so the contrast is between 
  # the baseline and the counterfactual changed interviewer age/gender
  mutate(b = 0 - b,
         ll = 0 - ll,
         ul = 0 - ul) %>%
  # Make plot
  ggplot(aes(outcome, 
             b, 
             colour = contrast,
             linetype = contrast)) +
    theme_linedraw() +
    geom_point(position = position_dodge(width = 0.8)) +
    geom_errorbar(aes(ymin = ll, ymax = ul),
                  position = position_dodge(width = 0.8),
                  width = 0.5) +
    scale_colour_manual(values = c("firebrick3", "black", "firebrick3", "black")) +
    scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
    coord_flip() +
    scale_y_continuous(breaks = seq(-0.2, 0.2, 0.05),
                     limits = c(-0.2, 0.2)) +
     theme(axis.title.y = element_blank(),
          legend.title = element_blank(),
          legend.position = "bottom",
          legend.text = element_text(size = 7),
          legend.key.width=unit(2,"line")) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    guides(colour = guide_legend(reverse = TRUE,
                                 ncol = 2),
           linetype = guide_legend(reverse = TRUE,
                                 ncol = 2)) +
    ylab("Contrasts of likelihood of policy domain prioritization \nSUR pooled OLS analysis with county fixed effects, 95% CIs")


```

```{r}
ggsave("figs/gottlieb_figs/gottlieb_contrasts_age_plot.png", gottlieb_contrasts_age_plot, height = 4, width = 8)
ggsave("figs/gottlieb_figs/gottlieb_contrasts_age_gender_plot.png", gottlieb_contrasts_age_gender_plot, height = 4.5, width = 8)
ggsave("figs/gottlieb_figs/gottlieb_models_plot.png", gottlieb_models_plot, height = 4, width = 7)
```


